Make any stupid plot you want

### 2021-01-25 draft/sections/math.tex
first example of total fiber that I'm gonna throw out

\section{Topological Artist Model}

In this section we introduce a mathematical description of the visualization pipeline where artist $\mathscr{A}$ functions transform data space $\mathscr{E}$ to an intermediate representation in a prerendered graphic space $\mathscr{H}$.

@@

\begin{figure}[ht!]
    \includegraphics[width=1\linewidth]{figures/math/fiberbundle.png}
    \label{fig:data_base_space}
    \caption{ The fiber $F$ is a continuous plane encoding the set of all possible (time, temperature) values.  The base space $K$ expresses that the fibers lie in continous space and therefore the data is continuous. The mapping $\pi:E\rightarrow K$ from total space to base space is what defines this structure as a fiber bundle. The continuous function $\tau_1$ returns a record in each fiber for each point on $K$; the set of all values $\tau_1$ returns is a dataset that lies in this fiberbundle. \textcolor{MidnightBlue}{remove one of the sections from this figure}} 
\end{figure}
The fiber bundle in figure~\ref{fig:data_base_space} is a representation of continuous (temperature, time) data. The fiber bundle abstraction facilitates seperately representing the time and temperature variables in the fiber $F$ and how these variables are connected in the base space $K$.  The function $\tau_1$ returns a record (temperature, time) for ever point on the interval $K$ and there can be many $\tau$ functions in the fiber bundle.

>>>>

\section{Topological Artist Model}
\note{can change this all to 3rd person passive later}\\
In this section we introduce a mathematical description of the visualization pipeline where artist $\mathscr{A}$ functions transform data space $\mathscr{E}$ to an intermediate representation in a prerendered graphic space $\mathscr{H}$.

@@

\begin{figure}[ht!]
    \includegraphics[width=.5\linewidth]{figures/math/fiberbundle.png}

    \caption{ The fiber $F$ is a continuous plane encoding the set of all possible (time, temperature) values.  The base space $K$ expresses that the fibers lie in continous space and therefore the data is continuous. The mapping $\pi:E\rightarrow K$ from total space to base space is what defines this structure as a fiber bundle. The continuous function $\tau_1$ returns a record in each fiber for each point on $K$; the set of all values $\tau_1$ returns is a dataset that lies in this fiberbundle. \note{remove one of the sections from this figure/maybe kill this example}}
    \label{fig:data_base_space} 
\end{figure}
The fiber bundle in figure~\ref{fig:data_base_space} is a representation of continuous (temperature, time) data. The fiber bundle abstraction facilitates seperately representing the time and temperature variables in the fiber $F$ and how these variables are connected in the base space $K$.  The function $\tau_1$ returns a record (temperature, time) for ever point on the interval $K$ and there can be many $\tau$ functions in the fiber bundle.
